---
title: "Building a galaxy tool with planemo"
author: "Florian Wuennemann"
date: "12/11/2020"
output: 
  rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

In this tutorial, I will describe how to construct a galaxy tool wrapper for a local galaxy installation from beginning to end. 

This walkthrough assumes you are using a local Galaxy via a Docker container from [galaxy-docker-stable](https://github.com/bgruening/docker-galaxy-stable). For this particular example, I am running [version 20.05](https://github.com/bgruening/docker-galaxy-stable/releases/tag/20.05) of the container on Ubuntu 20.04.1 LTS.

The tool we will create is going to be a wrapper for the R package [alevinQC](http://www.bioconductor.org/packages/release/bioc/html/alevinQC.html), which can be used to produce QC reports for runs of salmon-alevin. At the time of writing, no galaxy tool was available on galaxy toolshed and therefore I thought it was a good place to start with a fresh tool.

[Planemo tutorial website](https://planemo.readthedocs.io/en/latest/writing_standalone.html)

## Example run of alevinQC

Since alevinQC is an R package, here is a short example of a standard run. We require the output files from a salmon-alevin run. The package developers of alevinQC have kindly provided some example output files with alevinQC. Let's load them now and check that they are indeed available:

```{r}
library(alevinQC)
baseDir <- system.file("extdata/alevin_example_v0.14", package = "alevinQC")
checkAlevinInputFiles(baseDir = baseDir)
```

A standard run of alevinQC is also given as an example in the tutorial:

```{r, eval = TRUE}
outputDir <- tempdir()
alevinQCReport(baseDir = baseDir, sampleId = "testSample", 
               outputFile = "alevinQCReport.html", 
               outputFormat = "html_document",
               outputDir = ".", forceOverwrite = TRUE, quiet = FALSE)
```


## Setting up tool XML file

The first command we will run is used to setup a very basic template XML.

```{bash}
## More 
planemo tool_init --force \
  --id 'alevinQC_galaxy' \
  --name 'Produce QC reports for salmon-alevin runs'\
  --requirement bioconductor-alevinqc@1.6.0 \
  --example_command ' Rscript alevinQC.R' \
  --test_case \
  --cite_url 'https://github.com/csoneson/alevinQC' \
  --help_from_command 'alevinQC'
```

```{bash}
baseDir
  |--alevin
  |    |--featureDump.txt
  |    |--raw_cb_frequency.txt
  |    |--whitelist.txt  (depending on how alevin was run)
  |--aux_info
  |    |--meta_info.json
  |    |--alevin_meta_info.json
  |--cmd_info.json
```

